### 2004-11-10 Documentation/part1.tex
Parameter order sourcepower etc. corrected (WW)

While interacting with the user interface of \GLOBES , parameters are transferred to and from the \GLOBES\ library. In \GLOBES , one set of units 
for each type of quantity is used in order to avoid confusion about the definition of individual parameters. \tabl{units} summarizes the units of the most important quantities. In principle, the event rates are
proportional to the product of source power $\times$ target mass $\times$
 running time, which we call ``integrated luminosity''. Since especially the
 definition of the source power depends on the experiment type, the quantities of the three luminosity components
 are not unique and depend on the experiment definition. Usually,
 one uses detector masses in kilotons for beam experiments,
 and detector masses in tons for reactor experiments. Running times
 are normally given in years, where it is often assumed that the 
 experiment runs $100\%$ of the year. Thus, for shorter running periods,
 the running times need to be renormalized. Source powers are
 usually useful parent particle decays per year (neutrino factories,
 $\beta$-beams), target power in mega watts (superbeams), or thermal
 reactor power in giga watts (reactor experiments).
%
Since the pre-defined experiments in \tabl{experiments} are given for specific luminosities, it is useful to read out and change these
 parameters of the individual experiments:
\begin{function}
\GLBNS{SetSourcePower}
{\tt void glbSetSourcePower(double power, int exp, int fluxno)}
 sets the source power of experiment number {\tt exp} and flux number
 {\tt fluxno} to {\tt power}. The definition of the source power depends on the experiment type as described above.
\end{function}
\begin{function}
\GLBNS{GetSourcePower}
{\tt double glbGetSourcePower(int exp, int fluxno)}
 returns the source power of experiment number {\tt exp} and flux number
 {\tt fluxno}. 
\end{function}
\begin{function}
\GLBNS{SetRunningTime}
{\tt void glbSetRunningTime(double time, int exp, int fluxno)}
 sets the running time of experiment number {\tt exp} and flux number
 {\tt fluxno} to {\tt time} years.
\end{function}
\begin{function}
\GLBNS{GetRunningTime}
{\tt double glbGetRunningTime(int exp, int fluxno)}
 returns the running time of experiment number {\tt exp} and flux number
 {\tt fluxno}.
\end{function}
\begin{function}
 \GLBNS{SetTargetMass}
{\tt void glbSetTargetMass(double mass,int exp)}
sets the fiducial detector mass of experiment number {\tt exp} to {\tt mass} tons or kilotons (depending on the experiment definition).
\end{function}
\begin{function}
 \GLBNS{GetTargetMass}
{\tt double glbGetTargetMass(int exp)}
returns the fiducial detector mass of experiment number {\tt exp}.
\end{function}
Thus, these functions also demonstrate how to use the assigned experiment number and others. These numbers run from $0$ to the number of experiments-1, fluxes-1, \etc, where the individual elements are numbered in the order of their appearance. 
 Note that the source power and running time are quantities defined
together with the neutrino flux, whereas the target mass scales the whole
experiment. Thus, if one has, for instance, a neutrino and an antineutrino
running mode, one can scale them independently.

>>>>

While interacting with the user interface of \GLOBES , parameters are transferred to and from the \GLOBES\ library. In \GLOBES , one set of units 
for each type of quantity is used in order to avoid confusion about the definition of individual parameters. \tabl{units} summarizes the units of the most important quantities. In principle, the event rates are
proportional to the product of source power $\times$ target mass $\times$
 running time, which we call ``integrated luminosity''. Since especially the
 definition of the source power depends on the experiment type, the quantities of the three luminosity components
 are not unique and depend on the experiment definition. Usually,
 one uses detector masses in kilotons for beam experiments,
 and detector masses in tons for reactor experiments. Running times
 are normally given in years, where it is often assumed that the 
 experiment runs $100\%$ of the year. Thus, for shorter running periods,
 the running times need to be renormalized. Source powers are
 usually useful parent particle decays per year (neutrino factories,
 $\beta$-beams), target power in mega watts (superbeams), or thermal
 reactor power in giga watts (reactor experiments).
%
Since the pre-defined experiments in \tabl{experiments} are given for specific luminosities, it is useful to read out and change these
 parameters of the individual experiments:
\begin{function}
\GLBNS{SetSourcePower}
{\tt void glbSetSourcePower(int exp, int fluxno, double power)}
 sets the source power of experiment number {\tt exp} and flux number
 {\tt fluxno} to {\tt power}. The definition of the source power depends on the experiment type as described above.
\end{function}
\begin{function}
\GLBNS{GetSourcePower}
{\tt double glbGetSourcePower(int exp, int fluxno)}
 returns the source power of experiment number {\tt exp} and flux number
 {\tt fluxno}.
\end{function}
\begin{function}
\GLBNS{SetRunningTime}
{\tt void glbSetRunningTime(int exp, int fluxno, double time)}
 sets the running time of experiment number {\tt exp} and flux number
 {\tt fluxno} to {\tt time} years.
\end{function}
\begin{function}
\GLBNS{GetRunningTime}
{\tt double glbGetRunningTime(int exp, int fluxno)}
 returns the running time of experiment number {\tt exp} and flux number
 {\tt fluxno}.
\end{function}
\begin{function}
 \GLBNS{SetTargetMass}
{\tt void glbSetTargetMass(int exp, double mass)}
sets the fiducial detector mass of experiment number {\tt exp} to {\tt mass} tons or kilotons (depending on the experiment definition).
\end{function}
\begin{function}
 \GLBNS{GetTargetMass}
{\tt double glbGetTargetMass(int exp)}
returns the fiducial detector mass of experiment number {\tt exp}.
\end{function}
Thus, these functions also demonstrate how to use the assigned experiment number and others. These numbers run from $0$ to the number of experiments-1, fluxes-1, \etc, where the individual elements are numbered in the order of their appearance. 
 Note that the source power and running time are quantities defined
together with the neutrino flux, whereas the target mass scales the whole
experiment. Thus, if one has, for instance, a neutrino and an antineutrino
running mode, one can scale them independently.
